Clustering: A pipeline to analyse time-course gene expression data

### 2019-03-01 scripts/03_clustering.Rmd
FIX reactivating the max number of genes used for the clustering

# Differential expression analysis
timecourse_contrasts = c("C-K", "C-M")

@@

# Whether to filter genes
filter_genes = TRUE
keep_all_significant = TRUE
n_genes_to_keep = 5000
n_clusters = 20
percentage_genes_to_label = 0.5
```

@@

# Right now, the package doesn't contain the normalized data
pvalues = read.table(".results/pvalues.txt", sep="\t", check.names=FALSE)
```

@@

```{r}
if(filter_genes){
    # First, filter out any genes that doesn't have a log fold change of at
    # least 2
    # XXX I should actually filter on the max, but it is broken right now.
    lfc_col_to_keep = colnames(pvalues)[
	grepl("-lfc_max", colnames(pvalues))]
    pvalues = pvalues[rowSums(abs(pvalues[, lfc_col_to_keep]) > 2) > 0, ]

    if(dim(pvalues)[1] > n_genes_to_keep){

	# Then rank by fisher's p-value and take max the number of genes of
	# interest
	# Filter out q-values for the pvalues table
	pval_col_to_keep = colnames(pvalues)[grepl("-pval", colnames(pvalues))]
	pvalues = pvalues[, pval_col_to_keep]
	fishers_pval = moanin:::fisher_method(pvalues)
        if(keep_all_significant){
	   genes_to_keep = names(fishers_pval[fishers_pval < 0.05])
	}else{
	    genes_to_keep = names(sort(fishers_pval)[1:n_genes_to_keep])
	}
    }else{
	genes_to_keep = names(pvalues)
    }

    y = as.matrix(data[genes_to_keep, ])
}else{
    y = as.matrix(data)
}

>>>>

@@

# Whether to filter genes
filter_genes = TRUE
keep_all_significant = FALSE
n_genes_to_keep = 10000
n_clusters = 20
percentage_genes_to_label = 0.5
```

@@

# Right now, the package doesn't contain the normalized data
de_analysis = read.table(".results/pvalues.txt", sep="\t", check.names=FALSE)
```

@@

```{r filter_genes}
if(filter_genes){
    # First, filter out any genes that doesn't have a log fold change of at
    # least 2
    # XXX I should actually filter on the max, but it is broken right now.
    lfc_col_to_keep = colnames(de_analysis)[
	grepl("-lfc_max", colnames(de_analysis))]
    de_analysis = de_analysis[rowSums(abs(de_analysis[, lfc_col_to_keep]) > 2) > 0, ]

    if(dim(de_analysis)[1] > n_genes_to_keep){

	# Then rank by fisher's p-value and take max the number of genes of
	# interest
	# Filter out q-values for the pvalues table
	pval_col_to_keep = colnames(de_analysis)[grepl("-pval", colnames(de_analysis))]
	pvalues = de_analysis[, pval_col_to_keep]
	fishers_pval = moanin:::fisher_method(pvalues)
	fishers_qval = stats::p.adjust(fishers_pval)
        if(keep_all_significant){
	   genes_to_keep = names(fishers_qval[fishers_qval < 0.05])
	}else{
	    genes_to_keep = names(sort(fishers_pval)[1:n_genes_to_keep])
	}
    }else{
	genes_to_keep = names(pvalues)
    }

    y = as.matrix(data[genes_to_keep, ])
}else{
    y = as.matrix(data)
}
```

After filtering, we consider `r dim(y)[1]` genes for the clustering.

```{r clustering}
